---
title: "Poisson regression Thesis"
author: "Bo Havinga"
output: html_document
---

Import data
```{r}
BUYquarter <- read.csv("/Users/Bo/Documents/Universiteit RSM/Master/Thesis/Data/BUYquarter.csv")
```

Make subset with the converted customers
```{r}
BUYquarterID <- subset(BUYquarter, event == 1)
```

Add which year they buy
```{r}
BUYquarterID$buyquarter <- BUYquarterID$Start_Date + BUYquarterID$tstop #This is an extra variable that needs to be included in the model
BUYquarterID$buyquarter <- as.factor(BUYquarterID$buyquarter)

BUYquarterID$buyyear <- BUYquarterID$buyquarter 
year_buy <- c(`1` = 1, `2` = 1, `3` = 1,
              `4` = 1, `5` = 2, `6` = 2,
              `7` = 2, `8` = 2, `9` = 3,
              `10` = 3, `11` = 3)
library(plyr)
BUYquarterID$buyyear <- mapvalues(BUYquarterID$buyyear, from = names(year_buy), to = year_buy)

season <- c(`1` = 1, `2` = 2, `3` = 3,
              `4` = 4, `5` = 1, `6` = 2,
              `7` = 3, `8` = 4, `9` = 1,
              `10` = 2, `11` = 3)
BUYquarterID$season <- BUYquarterID$buyquarter
BUYquarterID$season <- mapvalues(BUYquarterID$buyquarter, from = names(season), to = season)
```

Remove outliers for dependent variable
```{r}
boxplot(BUYquarterID$revenue, yaxt="n")
Q1 <- quantile(BUYquarterID$revenue, .25)
Q3 <- quantile(BUYquarterID$revenue, .75)
IQR <- IQR(BUYquarterID$revenue)

BUYquarterID_out <- subset(BUYquarterID, BUYquarterID$revenue > (Q1 - 1.5*IQR) & BUYquarterID$revenue < (Q3 + 1.5*IQR))
dim(BUYquarterID_out)

boxplot(BUYquarterID_out$revenue, yaxt="n")
```

How many buys each year
```{r}
BUYquarterID_out$new_rev <- floor((BUYquarterID_out$revenue/CONFIDENTIAL INFORMATION))
sum(BUYquarterID_out$buyyear==1)
sum(BUYquarterID_out$buyyear==2)
sum(BUYquarterID_out$buyyear==3)

library(ggplot2)

ggplot(BUYquarterID_out, aes(x = new_rev)) +
  geom_bar(fill = "dark blue") +
  xlab("Dependent Variable: revenue_class") +
  ylab("Count for Each Revenue Class") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(color = "grey80")) +
  scale_x_continuous(breaks = unique(BUYquarterID_out$new_rev))


#Quickly add four rows to better interpreted
new_rows <- data.frame(matrix(0, nrow = 4, ncol = 52))
names(new_rows) <- names(BUYquarterID_out)
# set the values of buyyear and season to 1 for each row
new_rows$buyyear <- 1
new_rows$season <- 1

new_data <- rbind(BUYquarterID_out, new_rows)


# Year
ggplot(new_data, aes(x = buyyear)) +
  geom_bar(fill = "dark blue") +
  xlab("Buying Year") +
  ylab("Number of Converted Customers") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(color = "grey80"))
```

How many buys each quarter
```{r}
library(ggplot2)
ggplot(new_data, aes(x = buyquarter)) +
  geom_bar(fill = "dark blue") +
  xlab("New Dependent Variable of Revenue: new_rev") +
  ylab("Number of Converted Customers") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(color = "grey80"))

# Show season without 23 because Q4 is missing
BUYquarterID_2122 <- subset(new_data, buyyear == 1 | buyyear == 2)
season_order <- factor(BUYquarterID_2122$season, levels = c(1, 2, 3, 4))
ggplot(BUYquarterID_2122, aes(x = season_order))+
  geom_bar(fill = "dark blue") +
  xlab("Quarter of the Year") +
  ylab("Number of Converted Customers") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(color = "grey80"))

# Show season with 23
season_order2 <- factor(new_data$season, levels = c(1, 2, 3, 4))
ggplot(new_data, aes(x = season_order2))+
  geom_bar(fill = "dark blue") +
  xlab("Quarter of the Year") +
  ylab("Number of Converted Customers") +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(color = "grey80"))




```


Make new variable for revenue
```{r}
library(ggplot2)
ggplot(BUYquarterID_out, aes(x = new_rev)) +
  geom_bar()
```

Average deal size each year
```{r}
mean(BUYquarterID_out[BUYquarterID_out$buyyear == 1, "new_rev"])
mean(BUYquarterID_out[BUYquarterID_out$buyyear == 2, "new_rev"])
mean(BUYquarterID_out[BUYquarterID_out$buyyear == 3, "new_rev"])
mean(BUYquarterID_out$new_rev)
```

Make variables standadized
```{r}
BUYquarterID_out$Employees_s <- scale(BUYquarterID_out$Employees)
BUYquarterID_out$cross_selling_s <- scale(BUYquarterID_out$cross_selling)
BUYquarterID_out$apps_MAU_s <- scale(BUYquarterID_out$apps_MAU)
BUYquarterID_out$Avg.Interactions.per.Contact_s <- scale(BUYquarterID_out$Avg.Interactions.per.Contact)
BUYquarterID_out$Avg.Interactions.per.Contact_lag_s <- scale(BUYquarterID_out$Avg.Interactions.per.Contact_lag)
BUYquarterID_out$tstop_s <- scale(BUYquarterID_out$tstop)

BUYquarterID_out$digital_content_s <- scale(BUYquarterID_out$digital_content)
BUYquarterID_out$events_s <- scale(BUYquarterID_out$events)
BUYquarterID_out$trails_s <- scale(BUYquarterID_out$trails)
BUYquarterID_out$freemium_s <- scale(BUYquarterID_out$freemium)

BUYquarterID_out$digital_content_s_lag <- scale(BUYquarterID_out$digital_content_lag)
BUYquarterID_out$events_s_lag <- scale(BUYquarterID_out$events_lag)
BUYquarterID_out$trails_s_lag <- scale(BUYquarterID_out$trails_lag)
BUYquarterID_out$freemium_s_lag <- scale(BUYquarterID_out$freemium_lag)
```


# Check for correlation
```{r}
# Make datasets for correlation plot
BUYquarterID_outcor_s <- BUYquarterID_out[,c(53,55,54,56,59:62,58)]
BUYquarterID_outcorboth_s <- BUYquarterID_out[,c(53,55,54,56,59,63,60,64,61,65,62,66,58)]
# Rename columns
names(BUYquarterID_outcor_s)[1] = "employees"
names(BUYquarterID_outcor_s)[2] = "avg_apps_built"
names(BUYquarterID_outcor_s)[3] = "cross_selling"
names(BUYquarterID_outcor_s)[4] = "avg_interactions_per_employee"
names(BUYquarterID_outcor_s)[5] = "digital_content_downloads"
names(BUYquarterID_outcor_s)[6] = "event_attendees"
names(BUYquarterID_outcor_s)[7] = "requested_trials"
names(BUYquarterID_outcor_s)[8] = "freemium_users"
names(BUYquarterID_outcor_s)[9] = "end_time"

names(BUYquarterID_outcorboth_s)[1] = "employees"
names(BUYquarterID_outcorboth_s)[2] = "avg_apps_built"
names(BUYquarterID_outcorboth_s)[3] = "cross_selling"
names(BUYquarterID_outcorboth_s)[4] = "avg_interactions_per_employee"
names(BUYquarterID_outcorboth_s)[5] = "digital_content_downloads"
names(BUYquarterID_outcorboth_s)[6] = "digital_content_downloads_lag"
names(BUYquarterID_outcorboth_s)[7] = "event_attendees"
names(BUYquarterID_outcorboth_s)[8] = "event_attendees_lag"
names(BUYquarterID_outcorboth_s)[9] = "requested_trials"
names(BUYquarterID_outcorboth_s)[10] = "requested_trials_lag"
names(BUYquarterID_outcorboth_s)[11] = "freemium_users"
names(BUYquarterID_outcorboth_s)[12] = "freemium_users_lag"
names(BUYquarterID_outcorboth_s)[13] = "end_time"
# Make plots
library(corrplot)
corrplot(cor(BUYquarterID_outcor_s), type = "lower",  tl.col = "black", tl.srt = 5, tl.cex = 0.7, cl.cex = 0.7, number.cex = 0.7, addCoef.col = "black")
corrplot(cor(BUYquarterID_outcorboth_s), type = "lower",  tl.col = "black", tl.srt = 5, tl.cex = 0.7, cl.cex = 0.7, number.cex = 0.5, addCoef.col = "black")
```

Cluster some industries
```{r}
BUYquarterID_out$Industry[BUYquarterID_out$ID == 16305375] <- "Financial Services"
BUYquarterID_out$Industry[BUYquarterID_out$ID == 2668081] <- "Government"
BUYquarterID_out$Industry[BUYquarterID_out$ID == 1444620] <- "Education"
```


Poisson regressions with average of 50 seeds (training)
```{r}
RMSEdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
MAEdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
PseudoR2df <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 

# Loop through the set.seed values
for (seed in 1:50) {
  set.seed(seed)
  
  # Your existing code
  trainIndex<- BUYquarterID_out$new_rev %>%
  createDataPartition(p = 0.75, list = FALSE)
  training <- BUYquarterID_out[trainIndex,]
  testing <- BUYquarterID_out[-trainIndex,]
  
  models <- list(
    M0 = vglm(new_rev ~ 1, family = pospoisson(), data = training, model = TRUE),
  M1 = vglm(new_rev ~ segment + country + Industry, family = pospoisson(), data = training, model = TRUE),
  M2 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s, family = pospoisson(), data = training, model = TRUE),
  M3 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s, family = pospoisson(), data = training, model = TRUE),
  M4 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s, family = pospoisson(), data = training, model = TRUE),
  M5 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + tstop_s, family = pospoisson(), data = training, model = TRUE),
  M6 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + Avg.Interactions.per.Contact_lag_s + digital_content_s_lag + events_s_lag + trails_s_lag + tstop_s, family = pospoisson(), data = training, model = TRUE)
  )

  # Initialize empty vectors to store the metrics for this seed
  RMSE_seed <- c()
  MAE_seed <- c()
  PseudoR2_seed <- c()

  # Loop through the models and calculate the metrics for this seed
  for (model_name in names(models)) {
    predictions <- predict(models[[model_name]], newdata = testing, type = "response")
    RMSE_seed <- c(RMSE_seed, RMSE(predictions, testing$new_rev))
    MAE_seed <- c(MAE_seed, MAE(predictions, testing$new_rev))
    pseudo_r2 <- PseudoR2(models[[model_name]], "McFadden")
    PseudoR2_seed <- c(PseudoR2_seed, pseudo_r2)
  }
  
  new_rowRMSE <- data.frame(model1 = RMSE_seed[1],
                            model2 = RMSE_seed[2],
                            model3 = RMSE_seed[3],
                            model4 = RMSE_seed[4],
                            model5 = RMSE_seed[5],
                            model6 = RMSE_seed[6],
                            model7 = RMSE_seed[7])
  RMSEdf <- rbind(RMSEdf, new_rowRMSE)
  
  new_rowMAE <- data.frame(model1 = MAE_seed[1],
                           model2 = MAE_seed[2],
                           model3 = MAE_seed[3],
                           model4 = MAE_seed[4],
                           model5 = MAE_seed[5],
                           model6 = MAE_seed[6],
                           model7 = MAE_seed[7])
  MAEdf <- rbind(MAEdf, new_rowMAE)
  
  new_rowPseudoR2 <- data.frame(model1 = PseudoR2_seed[1],
                               model2 = PseudoR2_seed[2],
                               model3 = PseudoR2_seed[3],
                               model4 = PseudoR2_seed[4],
                               model5 = PseudoR2_seed[5],
                               model6 = PseudoR2_seed[6],
                               model7 = PseudoR2_seed[7])
  PseudoR2df <- rbind(PseudoR2df, new_rowPseudoR2)

}

# Create the dataframe
poissonfinal <- data.frame(Model = 1:7,
                           RMSE = c(mean(RMSEdf$model1), mean(RMSEdf$model2), mean(RMSEdf$model3),
                                    mean(RMSEdf$model4), mean(RMSEdf$model5), mean(RMSEdf$model6),
                                    mean(RMSEdf$model7)),
                           MAE = c(mean(MAEdf$model1), mean(MAEdf$model2), mean(MAEdf$model3),
                                    mean(MAEdf$model4), mean(MAEdf$model5), mean(MAEdf$model6),
                                    mean(MAEdf$model7)),
                           PseudoR2 = c(mean(PseudoR2df$model1), mean(PseudoR2df$model2), mean(PseudoR2df$model3),
                                        mean(PseudoR2df$model4), mean(PseudoR2df$model5), mean(PseudoR2df$model6),
                                        mean(PseudoR2df$model7)))

poissonfinal_xtab <- xtable(poissonfinal)
print(poissonfinal_xtab)
print(poissonfinal)

```



# T-test
```{r}
# Pairwise t-tests for RMSE
ttest_RMSE <- list()
pvalue_RMSE <- list()
for (i in 1:6) {
  ttest_RMSE[[i]] <- t.test(RMSEdf[[paste0("model", i)]], RMSEdf[[paste0("model", i + 1)]])
  pvalue_RMSE[[i]] <- ttest_RMSE[[i]]$p.value
}

# Pairwise t-tests for MAE
ttest_MAE <- list()
pvalue_MAE <- list()
for (i in 1:6) {
  ttest_MAE[[i]] <- t.test(MAEdf[[paste0("model", i)]], MAEdf[[paste0("model", i + 1)]])
  pvalue_MAE[[i]] <- ttest_MAE[[i]]$p.value
}

# Pairwise t-tests for R-squared
ttest_R2 <- list()
pvalue_R2 <- list()
for (i in 2:6) {
  ttest_R2[[i]] <- t.test(PseudoR2df[[paste0("model", i)]], PseudoR2df[[paste0("model", i + 1)]])
  pvalue_R2[[i]] <- ttest_R2[[i]]$p.value
}
t.test(AICdf[["model6"]], AICdf[["model7"]])$p.value

# Pairwise t-tests for AIC
ttest_AIC <- list()
pvalue_AIC <- list()
for (i in 1:6) {
  ttest_AIC[[i]] <- t.test(AICdf[[paste0("model", i)]], AICdf[[paste0("model", i + 1)]])
  pvalue_AIC[[i]] <- ttest_AIC[[i]]$p.value
}

# Pairwise t-tests for BIC
ttest_BIC <- list()
pvalue_BIC <- list()
for (i in 1:6) {
  ttest_BIC[[i]] <- t.test(BICdf[[paste0("model", i)]], BICdf[[paste0("model", i + 1)]])
  pvalue_BIC[[i]] <- ttest_BIC[[i]]$p.value
}

t.test(BICdf[[paste0("model", 3)]], BICdf[[paste0("model", 3 + 1)]])
# Create a dataframe with models as rows
model_names <- c("model1-model2", "model2-model3", "model3-model4", "model4-model5", "model5-model6", "model6-model7")

# Initialize an empty dataframe
comparison_df <- data.frame(Model = model_names, RMSE = NA, MAE = NA, PseudoR2 = NA) #, AIC = NA, BIC = NA

# Assign the metrics to the dataframe
comparison_df$RMSE[1:6] <- sapply(1:6, function(i) pvalue_RMSE[[i]])
comparison_df$MAE[1:6] <- sapply(1:6, function(i) pvalue_MAE[[i]])
comparison_df$PseudoR2[2:6] <- sapply(2:6, function(i) pvalue_R2[[i]])
#comparison_df$AIC[1:6] <- sapply(1:6, function(i) pvalue_AIC[[i]])
#comparison_df$BIC[1:6] <- sapply(1:6, function(i) pvalue_BIC[[i]])

# Print the resulting dataframe
comparison_df_xtab <- xtable(comparison_df)
print(comparison_df)
print(comparison_df_xtab)
```


# Change back
```{r}
BUYquarterID_out$Industry[BUYquarterID_out$ID == 16305375] <- "Software, Data & Platforms"
BUYquarterID_out$Industry[BUYquarterID_out$ID == 2668081] <- "Nonprofit & IGO"
BUYquarterID_out$Industry[BUYquarterID_out$ID == 1444620] <- "Nonprofit & IGO"
```


# Results best model
```{r}
  
M6 = vglm(new_rev ~ Industry + segment + country  + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + Avg.Interactions.per.Contact_lag_s + digital_content_s_lag + events_s_lag + trails_s_lag + tstop_s, family = pospoisson(), data = BUYquarterID_out)
summary(M6)
```


# Check for unobserved heterogeneity
```{r}
residuals <- residuals(M6, type = "pearson")
dispersion <- sum(residuals^2) / df.residual(M6)
test_statistic <- sum(residuals^2) / dispersion
1 - pchisq(test_statistic, df = df.residual(M6))
```





##### CHECK WITH OUTLIERS #######

# Without outliers included
```{r}
BUYquarterID$new_rev <- floor((BUYquarterID$revenue/10000))

BUYquarterID$Employees_s <- scale(BUYquarterID$Employees)
BUYquarterID$cross_selling_s <- scale(BUYquarterID$cross_selling)
BUYquarterID$apps_MAU_s <- scale(BUYquarterID$apps_MAU)
BUYquarterID$Avg.Interactions.per.Contact_s <- scale(BUYquarterID$Avg.Interactions.per.Contact)
BUYquarterID$Avg.Interactions.per.Contact_lag_s <- scale(BUYquarterID$Avg.Interactions.per.Contact_lag)
BUYquarterID$tstop_s <- scale(BUYquarterID$tstop)

BUYquarterID$digital_content_s <- scale(BUYquarterID$digital_content)
BUYquarterID$events_s <- scale(BUYquarterID$events)
BUYquarterID$trails_s <- scale(BUYquarterID$trails)
BUYquarterID$freemium_s <- scale(BUYquarterID$freemium)

BUYquarterID$digital_content_s_lag <- scale(BUYquarterID$digital_content_lag)
BUYquarterID$events_s_lag <- scale(BUYquarterID$events_lag)
BUYquarterID$trails_s_lag <- scale(BUYquarterID$trails_lag)
BUYquarterID$freemium_s_lag <- scale(BUYquarterID$freemium_lag)
```

# Check for correlation
```{r}
# Make datasets for correlation plot
BUYquarterID_outcor_s <- BUYquarterID_out[,c(53:56,59:62,58)]
BUYquarterID_outcorboth_s <- BUYquarterID_out[,c(53:56,59,63,60,64,61,65,62,66,58)]
# Make plots
library(corrplot)
corrplot(cor(BUYquarterID_outcor_s), type = "lower",  tl.col = "black", tl.srt = 35, tl.cex = 0.7, cl.cex = 0.7, number.cex = 0.7, addCoef.col = "black")
corrplot(cor(BUYquarterID_outcorboth_s), type = "lower",  tl.col = "black", tl.srt = 35, tl.cex = 0.7, cl.cex = 0.7, number.cex = 0.5, addCoef.col = "black", title = "\n\n Correlation Plot Of Poisson Data")
```

Merge categories for industry
```{r}
# Find the rows with the specified IDs
rows_to_change <- BUYquarterID$ID %in% c(1877638, 16305375)

# Change the Industry values for the specified rows
BUYquarterID$Industry[rows_to_change] <- c("Government", "Financial Services")
```

Poisson regressions with average of 50 seeds
```{r}
AICdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
BICdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
RMSEdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
MAEdf <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
PseudoR2df <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 
R2df <- data.frame(model1=as.integer(),model2=as.integer(),model3=as.integer(),model4=as.integer(),model5=as.integer(),model6=as.integer(),model7=as.integer()) 


# Loop through the set.seed values
for (seed in 1:50) {
  set.seed(seed)
  
  # Your existing code
  trainIndex<- BUYquarterID$new_rev %>%
  createDataPartition(p = 0.75, list = FALSE)
  training <- BUYquarterID[trainIndex,]
  testing <- BUYquarterID[-trainIndex,]
  
  models <- list(
    M0 = vglm(new_rev ~ 1, family = pospoisson(), data = training, model = TRUE),
  M1 = vglm(new_rev ~ segment + country + Industry, family = pospoisson(), data = training, model = TRUE),
  M2 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s, family = pospoisson(), data = training, model = TRUE),
  M3 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s, family = pospoisson(), data = training, model = TRUE),
  M4 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s, family = pospoisson(), data = training, model = TRUE),
  M5 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + tstop_s, family = pospoisson(), data = training, model = TRUE),
  M6 = vglm(new_rev ~ segment + country + Industry + Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + Avg.Interactions.per.Contact_lag_s + digital_content_s_lag + events_s_lag + trails_s_lag + tstop_s, family = pospoisson(), data = training, model = TRUE)
  )

  # Initialize empty vectors to store the metrics for this seed
  RMSE_seed <- c()
  MAE_seed <- c()
  PseudoR2_seed <- c()

  # Loop through the models and calculate the metrics for this seed
  for (model_name in names(models)) {
    predictions <- predict(models[[model_name]], newdata = testing, type = "response")
    RMSE_seed <- c(RMSE_seed, RMSE(predictions, testing$new_rev))
    MAE_seed <- c(MAE_seed, MAE(predictions, testing$new_rev))
    pseudo_r2 <- PseudoR2(models[[model_name]], "McFadden")
    PseudoR2_seed <- c(PseudoR2_seed, pseudo_r2)
  }
  
  new_rowRMSE <- data.frame(model1 = RMSE_seed[1],
                            model2 = RMSE_seed[2],
                            model3 = RMSE_seed[3],
                            model4 = RMSE_seed[4],
                            model5 = RMSE_seed[5],
                            model6 = RMSE_seed[6],
                            model7 = RMSE_seed[7])
  RMSEdf <- rbind(RMSEdf, new_rowRMSE)
  
  new_rowMAE <- data.frame(model1 = MAE_seed[1],
                           model2 = MAE_seed[2],
                           model3 = MAE_seed[3],
                           model4 = MAE_seed[4],
                           model5 = MAE_seed[5],
                           model6 = MAE_seed[6],
                           model7 = MAE_seed[7])
  MAEdf <- rbind(MAEdf, new_rowMAE)
  
  new_rowPseudoR2 <- data.frame(model1 = PseudoR2_seed[1],
                               model2 = PseudoR2_seed[2],
                               model3 = PseudoR2_seed[3],
                               model4 = PseudoR2_seed[4],
                               model5 = PseudoR2_seed[5],
                               model6 = PseudoR2_seed[6],
                               model7 = PseudoR2_seed[7])
  PseudoR2df <- rbind(PseudoR2df, new_rowPseudoR2)
}

# Create the dataframe
poissonfinal <- data.frame(Model = 1:7,
                           RMSE = c(mean(RMSEdf$model1), mean(RMSEdf$model2), mean(RMSEdf$model3),
                                    mean(RMSEdf$model4), mean(RMSEdf$model5), mean(RMSEdf$model6),
                                    mean(RMSEdf$model7)),
                           MAE = c(mean(MAEdf$model1), mean(MAEdf$model2), mean(MAEdf$model3),
                                    mean(MAEdf$model4), mean(MAEdf$model5), mean(MAEdf$model6),
                                    mean(MAEdf$model7)),
                           PseudoR2 = c(mean(PseudoR2df$model1), mean(PseudoR2df$model2), mean(PseudoR2df$model3),
                                        mean(PseudoR2df$model4), mean(PseudoR2df$model5), mean(PseudoR2df$model6),
                                        mean(PseudoR2df$model7)))

poissonfinal_xtab <- xtable(poissonfinal)
print(poissonfinal_xtab)
print(poissonfinal)
```



# Results best model (model 6)
```{r}
M6 = vglm(new_rev ~ Industry + segment + country +  Employees_s + apps_MAU_s + cross_selling_s + Avg.Interactions.per.Contact_s + digital_content_s + events_s + trails_s + freemium_s + Avg.Interactions.per.Contact_lag_s + digital_content_s_lag + events_s_lag + trails_s_lag + tstop_s, family = pospoisson(), data = BUYquarterID)
summary(M6)
```


# Check for unobserved heterogeneity
```{r}
residuals <- residuals(M6, type = "pearson")
dispersion <- sum(residuals^2) / df.residual(M6)
test_statistic <- sum(residuals^2) / dispersion
1 - pchisq(test_statistic, df = df.residual(M6))
```
